\documentclass[12pt, a4papre]{article}
\usepackage[catalan]{babel}
\usepackage[unicode]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{xifthen}

\newcommand{\norm}[1]{\lvert #1 \rvert}

\hypersetup{
    colorlinks = true,
    linkcolor = blue
}

\author{Igor Yuziv\\
	   Daniel Vilardell}
\title{\textbf{Human Values and Professional Ethics}}
\date{}

\begin{document}
	\maketitle
	
	The engineering field is about transformation and innovations, therefore ethics make up a big scope when it comes to change. That is why we have chosen this article to read, talk about and summarise.
	
	\section{Human values \& professional ethics}
	
	The study of engineering ethics in college or schools helps students prepare and be ready for major life challenges, since it develops widely applicable skills in communication, reasoning and reflection. These skills enhace student's get better with what they like and be better workers, alone and in group projects. 
	
	The ethical standards can be influenced by many factors:
	\begin{itemize}
		\item Ethical dilemas can bring up hard decisions in many projects.
		\item Technological advancements can require hard work and patience in order to keep up to date with the latest news.
		\item Moral values will take a crucial role in decision making.
		\item The people's safety can be in our hands and our responsibility.
	\end{itemize}
	
	\section{Professional Ethics}
	
	\textbf{\textcolor{blue}{Professionalism}} is defined as the conduct or qualities that characterise or mark a profession or professional. There are therefore some rules a professional should follow in order to behave appropriately in the engineering field. These are called the golden rules and are as follows.
	\begin{itemize}
		\item \textbf{Always strive for excellence:} In order to achieve success you have to aim as high as you can.
		\item \textbf{Be trustworthy:} As we have said in the previous section, people's safety can be in our hands and therefore people need to put trust in you.
		\item \textbf{Be accountable:} Stand tall and be counted for what actions you have undertaken.
		\item \textbf{Be respectful:} In order to make social interactions in the workplace run smoothly, avoid conflicts and earn respect by respecting others.
		\item \textbf{Be honest:} This is a virtue highly prized by employers and colleagues, for it builds trust and increases your personal value to all.
		\item \textbf{Be competent:} Do your job properly and try to learn every day in order to improve your performance.
	\end{itemize}
	
	\section{Work Ethics}
	
	\textbf{Work ethics:}  Set of attitudes concerned with the value of work, which forms the motivational orientation.
	
	The work ethics are aimed at ensuring the economy, productivity, safety, health and hygiene, privacy, security, cultural and social development, welfare, environment, and offer opportunities for all, according to their abilities, but without discrimination. \textcolor{blue}{Professional ethics} is the set of standards adopted by professionals.
	
	\section{Professional Values}
	
	\begin{itemize}
		\item \textbf{Integrity:} The unity of thought, word and deed and open mindedness. It helps them to earn self-respect and recognition by doing the job.
		\item \textbf{Credibility \& Responsibility:} Work in a transparent manner and accept responsibility for your actions.
		\item \textbf{Commitment:} Holding sustained interest and firmness with the fervent attitude and hope that one will achieve the goals, is commitment.
		\item \textbf{Attitude:} Positive Mental Attitude characterizes faith, integrity, hope, optimism, courage, initiative, generosity, tolerance and tact.
		\item \textbf{Valuing Time:} Time is rare resource. This resource is continuously spent, whether any decision or action is taken or not.
	\end{itemize}
	
	\section{Resources}
	
	The article choosen can be seen in \href{https://eng.rizvi.edu.in/wp-content/uploads/2020/04/Handbook-Human-Values-and-Professional-Ethics.pdf}{Human Values and Professional Ethics}

\end{document}